Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-05-09 Paper/paper.tex
9may_1

Second, we looked at 6 target proteins from the CASP9 experiment~\cite{Moult2011}.  For each target, we examined up to 5 submitted
models.  We computed the difference free energy between the true native and the best model.
Figure~\ref{fig:summary_casp} and Table~\ref{table:casp_control} show that, in 5 out of 6 cases, the confinement method
assigns a lower free energy to the experimentally determined structure than to any of the decoys.  Other well-known
discriminators can also successfully tell native structures from computer generated models~\cite{Sheffler2009,Zhou2002} 
; it is just an independent useful validation that the confinement calculations make
sense.

>>>>

Second, we looked at a series of protein structure which has a similar sequence but different fold and function. We 
investigated whether confinement method can predict their conformational preferences.
Third, we looked at 6 target proteins from the CASP9 experiment~\cite{Moult2011}.  For each target, we examined up to 5 submitted
models.  We computed the difference free energy between the true native and the best model.
Figure~\ref{fig:summary_casp} and Table~\ref{table:casp_control} show that, in 5 out of 6 cases, the confinement method
assigns a lower free energy to the experimentally determined structure than to any of the decoys.  Other well-known
discriminators can also successfully tell native structures from computer generated models~\cite{Sheffler2009,Zhou2002} 
; it is just an independent useful validation that the confinement calculations make
sense.
